Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-05-11 BD_radvel/kurosawa.tex
Minor changes.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@716 25464f21-6099-402c-b30a-640f1d40d38b
Worked on the Stu's comments (not finshed though). RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@718 25464f21-6099-402c-b30a-640f1d40d38b

\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{\apj}
\newcommand{\pasp}{PASP}
\newcommand{\aj}{AJ}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\aapr}{A\&AR}
\newcommand{\pasj}{PASJ}

@@

We present the results of a radial velocity (RV) survey of 14 brown
dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi dark
cloud core. We obtained high-resolution echelle spectra at VLT using
Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
epochs for each object, and measured the shifts in their RVs to
identify candidates for binary/multiple systems in the sample. The
average time separation of the RV measurements is 21.6~d, and our
survey is sensitive to the binaries with separation $<0.12$~au.  We
found 4 out of 17 objects (or $24^{+16}_{-14}$~per~cent by fraction)
show a significant RV change in 4--33~d time scale, and are 
considered as binary/multiple `candidates.'  We found no double-lined
spectroscopic binaries in our sample, based on the shape of
cross-correlation curves. The RV dispersion of the objects in UScoOB
is found to be very similar to that of the BD and VLM stars in
Chamaeleon~I (Cha~) previously studies by others. We also found the
distribution of the mean rotational velocities ($v\,\sin i$) of the
UScoOB objects is similar to that of the Cha~I, but the dispersion of
$v\,\sin i$ is significantly larger than that of the Cha~I objects.

@@

Most stars are member of binary systems and it is therefore important that
a complete star formation theory be able to predict the binary fraction,
period distribution, and mass-ratio distribution of newly born stellar
objects across a wide range of masses. Furthermore, the study of the individual
binary system is the only direct means to determine the fundamental
stellar properties such as stellar masses and radii.

Recent high-resolution imaging studies of young brown dwarfs (BDs)
and very low-mass (VLM) stars have placed strong constraints on binaries
with separations of $\sim1-100\,\mathrm{au}$. For example, Hubble
Space Telescope (\emph{HST}) observations of $\alpha$~Per and the
Pleiades indicates a binary fraction ($f$) of $>10$~per~cent with
a bias towards separations ($a$) of less than $15$~au, and a mass-ratio
($q$) of $>0.7$ \citep{martin:2003} for objects around and below
the hydrogen burning limit (see also \citealt{bouy:2006}). A similar
lack of wide binaries was found in the field T-dwarf study \citep{burgasser:2003},
while $f=15$~per~cent was determined by \citet{close:2003} using
the adaptive optics at Gemini North. They also found an upper limit
to the semimajor axis distribution of $\sim20\,\mathrm{au}$. An
\emph{HST} study of more than 80 field late M and L dwarfs \citep{gizis:2003}
indicated $f=15$~per~cent with separations in the range of 1.6--16~au.
For s small sample (12) of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
$f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
by using a similar imaging technique. More recently,
\citet{basri:2006}, combined with the results of earlier works, found
the upper limit of the overall binary fraction for VLM stars of
$26\pm10$~per~cent.

@@

The extensive imaging surveys provide excellent observational constraints
on wider BD+BD binaries, but it is now necessary to search for shorter
period BD+BD binaries systematically. Binaries with the separation
of less than 1~au are not resolved by current imaging techniques,
but will be detectable as spectroscopic binaries, providing the mass-ratio
is not too extreme, and velocity separation is large enough. The first
BD+BD spectroscopic binary, PPl~15  \citep{basri:1999}, showed a
double-peaked cross-correlation function with a maximum velocity separation
of $>70\,\kmps$. The binary was found to have an eccentric orbit
($e=0.4$) with a period of $\sim5.8\,\mathrm{d}$. \citet{basri:1999}
suggested that the formation process of substellar objects is biased
towards smaller separation binaries based on the short period of PPl~15
and the lack of Pleiades BD binaries with separations $>40\,\mathrm{au}$.
Note that the median separation of binaries with solar-type primaries
is 30~au \citet{duquennoy:1991}. Pioneering work on the RVs
of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
and \citet{joergens:2006} who found a several binary candidates;
however, the orbital parameters and masses of binaries remains
unknown because the follow-up spectroscopic monitoring is lacking
or still being undertaken. In addition to the follow-up observations,
the number of BDs and VLM star binary candidates needs to be increased
in order to have better statistics on short-period binary parameters.

The separation distribution of BD/VLM binaries is critical to understanding
their origin. There are two main models for the formation of BDs and
VLM stars: first, they formed in a similar manner to higher mass stars,
but from smaller-mass, denser molecular cloud core (e.g.~\citealt{padoan:2002});
second, BD/VLM objects have low masses because they are ejected from
the dense core in which they form via dynamical interactions in multiple
system, cutting off their accretion before they have reached stellar
masses (\citealt{reipurth:2001}; \citealt{bate:2002}). Alternatively,
there is a third model in which a free-floating BD or planetary-mass
object can be formed in the process of the photo-evaporation \citep{whitworth:2004} with
the outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
removed by the strong radiation pressure from the nearby massive OB
 stars before the accretion onto the protostar at core centre
occurs.

Due to the dynamical interaction involved in the second model, BD/VLM
binaries that survive are generally expected to have small separations.
In the first model, wider binaries may be expected to be more common.
\citet{bate:2002} suggested that close binaries ($a<10\,\mathrm{au}$)
do not form directly, but result from hardening of wider systems though
a combination of dynamical interactions, accretion and interactions
with circum-binary discs. If BD/VLM binaries have formed through such
mechanisms, one would not expect to find binaries with 1--10~au separations
without also finding many with separation $<1$~au. If an absence/rarity
of binaries with 1~au were found, it would support the idea that
they are ejected quickly from multiple systems before they have undergone
the interactions that shorten their periods.

@@

\begin{tabular}{llcccc}
\hline 
Object&
Sp.&
mass&
RV&
$v\sin i$&
Known multiple?\tabularnewline
&
&
$\left[\mathrm{M_{\odot}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
$\mathrm{M7^{c}}$&
$0.07^{\mathrm{d}}$&
$-6.3\pm1.9^{\mathrm{d}}$&
$16.8\pm2.7^{\mathrm{d}}$&
no\tabularnewline
GY 141&
$\mathrm{M8.5^{a}}$&
$0.02^{\mathrm{d}}$&
\ldots{}&
$6.0^{f}$&
no\tabularnewline
GY 310&
$\mathrm{M8.5^{c}}$&
$0.08^{\mathrm{a,d}}$&
\ldots{}&
$10.0^{f}$&
no\tabularnewline
USco 40&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$37.5^{f}$&
no\tabularnewline
USco 53&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$45.0^{f}$&
no\tabularnewline
USco 55&
$\mathrm{M5.5^{b}}$&
$0.10+0.07^{\mathrm{e}}$&
\ldots{}&
$12.0^{f}$&
$\mathrm{yes^{e}}$\tabularnewline
USco 66&
$\mathrm{M6^{b}}$&
$0.07+0.07^{\mathrm{e}}$&
$-4.4\pm0.6^{\mathrm{d}}$&
$27.5^{f}$&
$\mathrm{yes^{e}}$\tabularnewline
USco 67&
$\mathrm{M5.5^{b}}$&
$0.10^{\mathrm{e}}$&
\ldots{}&
$18.0^{f}$&
no\tabularnewline
USco 75&
$\mathrm{M6^{b}}$&
$0.07^{\mathrm{e}}$&
$-5.6\pm1.1^{\mathrm{d}}$&
$63.0^{f}$&
no\tabularnewline
USco 100&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.9\pm0.6^{\mathrm{d}}$&
$50.0^{f}$&
no\tabularnewline
USco 101&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
\ldots{}&
no\tabularnewline
USco 104&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
$16.0^{f}$&
no\tabularnewline
USco 109&
$\mathrm{M6^{b}}$&
$0.07+0.04^{\mathrm{e}}$&
$-3.8\pm0.7^{\mathrm{d}}$&
$6.0^{f}$&
$\mathrm{yes^{e}}$\tabularnewline
USco 112&
$\mathrm{M5.5^{b}}$&
$0.1^{\mathrm{e}}$&
\ldots{}&
$8.0^{f}$&
no\tabularnewline
USco 121&
$\mathrm{M6^{b}}$&
$0.02^{\mathrm{b}}$&
$-38.9\pm1.0^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
USco 128&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-3.0\pm1.6^{\mathrm{d}}$&
$0.0^{f}$&
no\tabularnewline
USco 130&
$\mathrm{M7.5^{e}}$&
$0.04^{\mathrm{e}}$&
\ldots{}&
$14.0^{f}$&
no\tabularnewline
USco 132&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.2\pm1.1^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
\hline
\end{tabular}

@@

For each object and for each RV measurement, the deviations ($\Delta\mathrm{RV}$)
from the average RV are computed and summarized in Fig.~\ref{fig:radvel01}
along with their uncertainties ($\sigma_{\mathrm{RRV}}$) in order
to aid the identification of multiplicity candidates. Note that in
computing $\Delta\mathrm{RV}$ we do not require the knowledge of
absolute radial velocities, but only the relative
velocities (with respect to a template).

@@

According to the hydrodynamical simulations of a low-mass star-forming
cluster of \cite{bate:2003} which yields a stellar density of
$1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
of the stars and the BDs is $1.2\,\kmps$.  Similarly for the model
with a higher stellar density ($2.6\times10^{3}\,\mathrm{stars\,
pc^{-3}}$), the rms dispersion is 2.5~$\kmps$
(\citealt{bate:2005}). The standard deviation of
$\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our analysis is more
comparable the lower stellar density model.

@@

The range of $v\,\sin i$ found among our objects is $3.6$--$55.6\,\kmps$,
and a similar range is also found by \citet{mohanty:2005}. 
Fig.~\ref{fig:vrot_histrogram} shows the histogram
of $v\,\sin i$ distribution for the UScoOB objects (14 objects excluding
USco 121, non member). The log-normal fit of this distribution gives
the peak position at $16.9\,\kmps$ with a standard deviation $\sigma=27.8\,\kmps$.
Using the $v\,\sin i$ data in \citet{joergens:2001}, the same histogram
bin size used for UScoOB obects and the log-normal fit, we find the
$v\,\sin i$ distribution of the BD and VLM stars (8 objects) in Cha~I
peaks at $15.4\,\kmps$, and has the standard deviation of $8.0\,\kmps$.
The peak of the distribution is similar to that of Upper Sco objects,
but the standard deviation of the distribution is significantly smaller
than that of our Upper Sco objects. The difference maybe due to the
very small sample. A similar fit was applied to the $v\,\sin i$
distribution of 14 T~Tauri stars in Cha~I using the data of \citet{joergens:2001},
and we found a peak at $17.0\,\kmps$ with a  standard deviation
$25.9\,\kmps$ which are very similar to those of the Upper Sco brown
dwarf candidates and VLM stars.

@@

In Section~\ref{sub:Radial-velocities}, we found 4 out of 17
(excluding USco~121; non-member) objects show a statistically
significant RV variation, indicating that they are binary/multiple
candidates. In order to estimate the uncertainty in the
binary/multiple fraction from this relatively small sample, we will
follow the method used by \citet{basri:2006} who considered the binomial
distribution, $P_{B}\left ( x, n, p \right )$ of $x$ positive event
out of $n$ trials with the probability $p$ for a positive event in each
trial. In our case, $n=17$ (the number sample)  and $p=4/17=0.24$
(the fraction of binary/multiple).  The uncertainties was estimated by
plotting $P_{B}\left ( x, 17, 0.24 \right )$, and finding the values
of $x$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
analysis, we find the binary/multiple fraction along with the
uncertainties of our sample to be $f=24^{+16}_{-14}$~per~cent.

@@

There are six basic parameters our Monte Carlo simulation: 
primary mass ($M_{1}$), mass ratio ($q$), eccentricity
($e$), orbital phase ($\phi$), orbital inclination ($i$),
longitude of periastron ($\lambda$). The primary mass $M_{1}$ is
assigned from the adopted mass of 
the targets in Table~\ref{tab:literatures}, with a uniform random
deviation of $\pm0.002\,M_{\sun}$. The mass ratio is assumed to be
uniformly distributed between $q=0$ and $0.2$. The eccentricity $e$ is
assumed to be zero (circular orbits).  Both \citet{maxted:2005}
and \citet{basri:2006} found the detection probability is insensitive
to the assumed distribution of $q$ and $e$. The orbital phase is
randomly chosen between 0 and 1.  The inclination $i$ is randomly
chosen from the cumulative distribution of $\cos{i}$. The longitude of
periastron $\lambda$ is not necessary since we assumed $e=0$.

In order to compute the detection probability as a function of
semimajor axis $a$, we take the following procedure: (1)~for each
object in our targets, we randomly select $10^5$ binaries using the
assumption stated above for a given value of $a$, and compute the RV
of the primary ($V_{1}$), (2)~evolve the orbit by the time separation
of the RV measuremets use in the observations for this object, and
take another simulated measurement of RV ($V_{2}$), (3)~from $V_{1}$,
$V_{2}$ and the average uncertainty in RV ($\sigma_{\mathrm{RRV}}$)
from the observations, we compute the $\chi^{2}$ probability $p$,  and
flag the trial as a detection if $p<10^{-3}$ as done for the real
data, (4)~find the fraction of detections out of all random trials,
(5) repeat 1--4 for the range of $a$ between $10^{-3}$~and 10~au, and
(6) repeat 5 for the all targets, and find the detection probability
averaged over all targets as a function of $a$.

The result of the simulation is shown in
Fig.~\ref{fig:detect_prob}. The detection probability curve shown here
is very similar that of \citet{basri:2006} for a constant time
separation (20~d) case (see their Fig.~4). The probability remains
fairly constant up to  $a \approx 0.1\,\mathrm{au}$, and it rapidly
decreases beyond $a\approx 0.3\,\mathrm{au}$.  This turning point will
increase if we had used larger time separations in our observation. 
From this figure, we find that the 80~per~cent detection probability
up to for binaries with $a<0.12\,\mathrm{au}$, given our time
separations and the average uncertainty ($\sim0.5\,\kmps$) in the RV
measurements.

@@

\caption{The binary detection probability (solid) as a function of the semimajor
  axis ($a$), based on Monte~Carlo simulations of RV measurements, is
  shown.  For each object in our target list, the simulation was performed
  using the time separation ($\Delta t$) actually used in our
  two-epoch observations (c.f.~Table~\ref{tab:summary_results}) and
  the estimated primary mass  (c.f.~Table~\ref{tab:literatures}).  The
  final detection probability is obtained by averaging
  over the simulated observations of all the objects.  The average
  time separation in the two-epoch observations  is $\sim
  21.6\,\mathrm{d}$, and the average uncertainty in RV is
  $~0.5\,\kmps$. The probability remains fairly
  constant up to $a \approx 0.1\,\mathrm{au}$, and it rapidly decreases
  beyond $a\approx 0.3\,\mathrm{au}$.  The 80~per~cent detection
  probability is achieved for binaries with $a<0.12\,\mathrm{au}$. }

@@

We have presented two-epoch RV survey of 18 young BDs and VLM stars
($0.02~M_{\sun} < M_{*} < 0.1~M_{\sun}$) in
UScoOB and $\rho$~Oph dark cloud core using the high resolution UVES
echelle spectroscopy at VLT.  The average time separation of RV
measurements are 21.6~d, and our RV survey is sensitive to binaries
with separation smaller than 0.12~au.  One of our targets, USco~121, is
most likely a non-member of the UScoOB association based on the
deviation of the RV from the result of the population in the
association. A similar conclusion was found by \citet{muzerolle:2003}
from their RV study and the low lithium abundance.

>>>>

\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{\apj}
\newcommand{\pasp}{PASP}
\newcommand{\aj}{AJ}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\aapr}{A\&AR}
\newcommand{\pasj}{PASJ}
\newcommand{\nat}{Nat}

@@

We present the results of a radial velocity (RV) survey of 14 brown
dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi dark
cloud core. We obtained high-resolution echelle spectra at the VLT using
Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
epochs for each object, and measured the shifts in their RVs to
identify candidates for binary/multiple systems in the sample. The
average time separation of the RV measurements is 21.6~d, and our
survey is sensitive to the binaries with separation $<0.1$~au.  We
found 4 out of 17 objects (or $24^{+16}_{-13}$~per~cent by fraction)
show a significant RV change in 4--33~d time scale, and are 
considered as binary/multiple `candidates.'  We found no double-lined
spectroscopic binaries in our sample, based on the shape of
cross-correlation curves. The RV dispersion of the objects in UScoOB
is found to be very similar to that of the BD and VLM stars in
Chamaeleon~I (Cha~). We also found the distribution of the mean
rotational velocities ($v\,\sin i$) of the 
UScoOB objects is similar to that of the Cha~I, but the dispersion of
$v\,\sin i$ is much larger than that of the Cha~I objects.

@@

Most stars are member of binary systems and it is therefore important that
a complete star formation theory be able to predict the binary fraction,
period distribution, and mass-ratio distribution of  stellar
objects across a wide range of masses. Furthermore, the study of individual
binary systems is the only direct means to determine fundamental
stellar properties such as stellar masses and radii.

Recent high-resolution imaging studies of brown dwarfs (BDs)
and very low-mass (VLM) stars have placed strong constraints on binaries
with separations of $\sim1-100\,\mathrm{au}$. For example, Hubble
Space Telescope (\emph{HST}) observations of $\alpha$~Per and the
Pleiades indicates a binary fraction ($f$) of $>10$~per~cent with
a bias towards separations ($a$) of less than $15$~au, and a mass-ratio
($q$) of $>0.7$ \citep{martin:2003} for objects around and below
the hydrogen burning limit (see also \citealt{bouy:2006}). A similar
lack of wide binaries was found in the field T-dwarf study \citep{burgasser:2003},
while $f\approx15$~per~cent was determined by \citet{close:2003} using
the adaptive optics at Gemini North. They also found the vast majority
of systems have a semimajor axis $<20\,\mathrm{au}$ (see also
\citealt{siegler:2005} but \citealt{luhman:2004}). An
\emph{HST} study of more than 80 field late M and L dwarfs \citep{gizis:2003}
indicated $f\approx15$~per~cent with separations in the range of 1.6--16~au.
For a small (12) sample of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
$f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
by using a similar imaging technique. More recently,
\citet{basri:2006}, combined with the results of earlier works, found
the upper limit of the overall binary fraction for VLM stars of
$26\pm10$~per~cent.

@@

The extensive imaging surveys provide excellent observational constraints
on wider BD+BD binaries, but it is now necessary to search for shorter
period BD+BD binaries systematically. Binaries with the separation
of less than 1~au are not resolved by current imaging techniques,
but will be detectable as spectroscopic binaries, providing the mass-ratio
is not too extreme, and velocity separation is large enough. The first
BD+BD spectroscopic binary, PPl~15  \citep{basri:1999}, showed a
double-peaked cross-correlation function with a maximum velocity separation
of $>70\,\kmps$. The binary was found to have an eccentric orbit
($e=0.4$) with a period of $\sim5.8\,\mathrm{d}$. \citet{basri:1999}
suggested that the formation process of substellar objects is biased
towards smaller separation binaries based on the short period of PPl~15
and the lack of Pleiades BD binaries with separations $>40\,\mathrm{au}$.
Note that the median separation of binaries with solar-type primaries
is 30~au \citep{duquennoy:1991}. Pioneering works on the RVs
of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
and \citet{joergens:2006} who found a several binary candidates;
however, the orbital parameters and masses of binaries remains
unknown because the follow-up spectroscopic monitoring is lacking
or still being undertaken. In addition to the follow-up observations,
the number of BDs and VLM star binary candidates needs to be increased
in order to have better statistics on short-period binary parameters.

The first BD+BD eclipsing binary (2MASS J0532184--J0546085) was
discovered by \citet*{stassun:2006} from the $I$-band photometric
monitoring of the system. Combining their light curves and the results
from the follow-up radial velocity measurements, they were able to determined
the precise oribital and physical parameters of the system.  The projected
semimajor axis and the period of the binary are found as
$0.0398\pm0.0010$~au and $9.779621\pm0.000042$~d respectively.

The separation distribution of BD/VLM binaries is critical to
understanding their origin. There are two main models for the
formation of BDs and VLM stars: first, they have low masses because
they form in low-mass, dense molecular cloud cores
(e.g.~\citealt{padoan:2002}); second, BD/VLM objects have low masses
because they are ejected from the dense core in which they form via
dynamical interactions in multiple system, cutting off their accretion
before they have reached stellar masses (\citealt{reipurth:2001};
\citealt*{bate:2002}). Alternatively, there is a third model in which
a free-floating BD or planetary-mass object can be formed in the
process of the photo-evaporation
(e.g.~\citealt{mccaughrean:2002};~\citealt{whitworth:2004}) with  
the outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
removed by the strong radiation pressure from the nearby massive OB
stars before the accretion onto the protostar at core centre occurs.

Due to the dynamical interaction involved in the second model, BD/VLM
binaries that survive are generally expected to have small separations.
In the first model, wider binaries may be expected to be more common.
\citet*{bate:2002b} suggested that close binaries ($a<10\,\mathrm{au}$)
do not form directly, but result from hardening of wider systems though
a combination of dynamical interactions, accretion and interactions
with circum-binary discs. If BD/VLM binaries have formed through such
mechanisms, one would not expect to find binaries with 1--10~au separations
without also finding many with separation $<1$~au. If an absence/rarity
of binaries with 1~au were found, it may support the idea that
they are ejected quickly from multiple systems before they have undergone
the interactions that shorten their periods.

@@

\begin{tabular}{llcccc}
\hline 
Object&
Sp.&
mass&
RV&
$v\sin i$&
Known multiple?\tabularnewline
&
&
$\left[\mathrm{M_{\odot}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
$\mathrm{M7^{c}}$&
$0.07^{\mathrm{d}}$&
$-6.3\pm1.9^{\mathrm{d}}$&
$16.8\pm2.7^{\mathrm{d}}$&
no\tabularnewline
GY 141&
$\mathrm{M8.5^{a}}$&
$0.02^{\mathrm{d}}$&
\ldots{}&
$6.0^{f}$&
no\tabularnewline
GY 310&
$\mathrm{M8.5^{c}}$&
$0.08^{\mathrm{a,d}}$&
\ldots{}&
$10.0^{f}$&
no\tabularnewline
USco 40&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$37.5^{f}$&
no\tabularnewline
USco 53&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$45.0^{f}$&
no\tabularnewline
USco 55&
$\mathrm{M5.5^{b}}$&
$0.10+0.07^{\mathrm{e}}$&
\ldots{}&
$12.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 66&
$\mathrm{M6^{b}}$&
$0.07+0.07^{\mathrm{e}}$&
$-4.4\pm0.6^{\mathrm{d}}$&
$27.5^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 67&
$\mathrm{M5.5^{b}}$&
$0.10^{\mathrm{e}}$&
\ldots{}&
$18.0^{f}$&
no\tabularnewline
USco 75&
$\mathrm{M6^{b}}$&
$0.07^{\mathrm{e}}$&
$-5.6\pm1.1^{\mathrm{d}}$&
$63.0^{f}$&
no\tabularnewline
USco 100&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.9\pm0.6^{\mathrm{d}}$&
$50.0^{f}$&
no\tabularnewline
USco 101&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
\ldots{}&
no\tabularnewline
USco 104&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
$16.0^{f}$&
no\tabularnewline
USco 109&
$\mathrm{M6^{b}}$&
$0.07+0.04^{\mathrm{e}}$&
$-3.8\pm0.7^{\mathrm{d}}$&
$6.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 112&
$\mathrm{M5.5^{b}}$&
$0.1^{\mathrm{e}}$&
\ldots{}&
$8.0^{f}$&
no\tabularnewline
USco 121&
$\mathrm{M6^{b}}$&
$0.02^{\mathrm{b}}$&
$-38.9\pm1.0^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
USco 128&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-3.0\pm1.6^{\mathrm{d}}$&
$0.0^{f}$&
no\tabularnewline
USco 130&
$\mathrm{M7.5^{e}}$&
$0.04^{\mathrm{e}}$&
\ldots{}&
$14.0^{f}$&
no\tabularnewline
USco 132&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.2\pm1.1^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
\hline
\end{tabular}

@@

For each object and for each RV measurement, the deviations ($\Delta\mathrm{RV}$)
from the average RV are computed and summarized in Fig.~\ref{fig:radvel01}
along with their uncertainties ($\sigma_{\mathrm{RRV}}$) in order
to aid the identification of multiplicity candidates. Note that in
computing $\Delta\mathrm{RV}$ we do not require the knowledge of
absolute radial velocities, but only the relative
velocities (with respect to a template). 
Alternatively, we also computed the cross-correlation functions of
spectra of a same object (instead of using the spectra of the template
LHS~49) from two different epochs in order to find
$\Delta\mathrm{RV}$. The resulting cross-correlation functions were
found to be too noisy (due to the relatively low S/N in the object
spectra), and the peak positions of the cross-correlation curves were
not reliably located.

@@

According to the hydrodynamical simulations of a low-mass star-forming
cluster of \cite{bate:2003} which yields a stellar density of
$\sim10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
of the stars and the BDs is $1.2\,\kmps$.  Similarly for the model
with a higher stellar density ($\sim10^{4}\,\mathrm{stars\,
pc^{-3}}$), the rms dispersion is 2.5~$\kmps$
(\citealt{bate:2005}). The standard deviation of
$\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our analysis is more
comparable the lower stellar density model.

@@

The range of $v\,\sin i$ found among our objects is $3.6$--$55.6\,\kmps$,
and a similar range is also found by \citet{mohanty:2005}. 
Fig.~\ref{fig:vrot_histrogram} shows the histogram
of $v\,\sin i$ distribution for the UScoOB objects (14 objects excluding
USco 121, non member). The log-normal fit of this distribution gives
the peak position at $16.9\,\kmps$ with a standard deviation $\sigma=27.8\,\kmps$.
Using the $v\,\sin i$ data in \citet{joergens:2001}, the same histogram
bin size used for UScoOB obects and a log-normal fit, we find the
$v\,\sin i$ distribution of the BD and VLM stars (8 objects) in Cha~I
peaks at $15.4\,\kmps$, and has the standard deviation of $8.0\,\kmps$.
The peak of the distribution is similar to that of Upper Sco objects,
but the standard deviation of the distribution is much smaller
than that of our Upper Sco objects. The difference maybe due to the
very small sample. A similar fit was applied to the $v\,\sin i$
distribution of 14 higher mass T~Tauri stars in Cha~I using the data
of \citet{joergens:2001}, and we found a peak at $17.0\,\kmps$ with a
standard deviation $25.9\,\kmps$ which are very similar to those of
the Upper Sco brown dwarf candidates and VLM stars.

@@

In Section~\ref{sub:Radial-velocities}, we found 4 out of 17
(excluding USco~121; non-member) objects show a statistically
significant RV variation, indicating that they are binary/multiple
candidates. In order to estimate the uncertainty in the
binary/multiple fraction from this relatively small sample, we will
follow the method used by \citet{basri:2006} who considered the binomial
distribution, $P_{B}\left ( x, n, p \right )$ of $x$ positive event
out of $n$ trials with the probability $p$ for a positive event in each
trial. In our case, $n=17$ (the number of sample)  and $p=4/17=0.24$
(the fraction of binary/multiple).  The uncertainties was estimated by
plotting $P_{B}\left ( x, 17, 0.24 \right )$, and finding the values
of $x$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
analysis, we find the binary/multiple fraction along with the
uncertainties of our sample to be $f=24^{+16}_{-13}$~per~cent.

@@

There are six basic parameters in our Monte Carlo simulation: 
primary mass ($M_{1}$), mass ratio ($q$), eccentricity
($e$), orbital phase ($\phi$), orbital inclination ($i$),
longitude of periastron ($\lambda$). The primary mass $M_{1}$ is
assigned from the adopted mass of 
the targets in Table~\ref{tab:literatures}, with a uniform random
deviation of $\pm0.002\,M_{\sun}$. The mass ratio is assumed to be
uniformly distributed between $q=0$ and $0.2$. The eccentricity $e$ is
assumed to be zero (circular orbits).  Both \citet{maxted:2005}
and \citet{basri:2006} found the detection probability is insensitive
to the assumed distribution of $q$ and $e$. The orbital phase is
randomly chosen between 0 and 1.  The inclination $i$ is randomly
chosen from the cumulative distribution of $\cos{i}$. The longitude of
periastron $\lambda$ is not necessary since we assumed $e=0$.

In order to compute the detection probability as a function of
semimajor axis $a$, we take the following procedure: (1)~for each
object in our targets, we randomly select $10^5$ binaries using the
assumption stated above for a given value of $a$, and compute the RV
of the primary ($V_{1}$), (2)~evolve the orbit by the time separation
of the RV measuremets used in the observations for this object, and
take another simulated measurement of RV ($V_{2}$), (3)~from $V_{1}$,
$V_{2}$ and the average uncertainty in RV ($\sigma_{\mathrm{RRV}}$)
from the observations, we compute the $\chi^{2}$ probability $p$,  and
flag the trial as a detection if $p<10^{-3}$ as done for the real
data, (4)~find the fraction of detections out of all random trials,
(5) repeat 1--4 for the range of $a$ between $10^{-3}$~and 10~au, and
(6) repeat 5 for the all targets, and find the detection probability
averaged over all targets as a function of $a$.

The result of the simulation is shown in
Fig.~\ref{fig:detect_prob}. The detection probability curve shown here
is very similar that of \citet{basri:2006} for a constant time
separation (20~d) case (see their Fig.~4). The probability remains
fairly constant up to  $a \approx 0.1\,\mathrm{au}$, and it rapidly
decreases beyond $a\approx 0.3\,\mathrm{au}$.  This turning point will
increase if we had used larger time separations in our observation. 
From this figure, we find that the 80~per~cent detection probability
up to for binaries with $a<0.1\,\mathrm{au}$, given our time
separations and the average uncertainty ($\sim0.5\,\kmps$) in the RV
measurements.

@@

\caption{The binary detection probability (solid) as a function of the semimajor
  axis ($a$), based on Monte~Carlo simulations of RV measurements, is
  shown.  For each object in our target list, the simulation was performed
  using the time separation ($\Delta t$) actually used in our
  two-epoch observations (c.f.~Table~\ref{tab:summary_results}) and
  the estimated primary mass  (c.f.~Table~\ref{tab:literatures}).  The
  final detection probability is obtained by averaging
  over the simulated observations of all the objects.  The average
  time separation in the two-epoch observations  is $\sim
  21.6\,\mathrm{d}$, and the average uncertainty in RV is
  $~0.5\,\kmps$. The probability remains fairly
  constant up to $a \approx 0.1\,\mathrm{au}$, and it rapidly decreases
  beyond $a\approx 0.3\,\mathrm{au}$.  The 80~per~cent detection
  probability is achieved for binaries with $a<0.1\,\mathrm{au}$. }

@@

We have presented two-epoch RV survey of 18 young BDs and VLM stars
($0.02~M_{\sun} < M_{*} < 0.1~M_{\sun}$) in
UScoOB and $\rho$~Oph dark cloud core using the high resolution UVES
echelle spectroscopy at VLT.  The average time separation of RV
measurements are 21.6~d, and our RV survey is sensitive to binaries
with separation smaller than 0.1~au.  One of our targets, USco~121, is
most likely a non-member of the UScoOB association based on the
deviation of the RV from the result of the population in the
association. A similar conclusion was found by \citet{muzerolle:2003}
from their RV study and the low lithium abundance.
